Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-10-24 RR_manuscript/Draft_RR.Rmd

<!-- TODO: add background info and use consistent terminology -->
This section deals with the meta-analytic analysis of the results submitted by the teams.
<!-- TODO: repeat exclusion criteria -->
First, we report on the between-team variability estimate (i.e. the meta-analytic group-level standard deviation $\sigma_{\alpha_{\text{t}}}$), which is the focus of this study, followed by the meta-analytic estimate (i.e. the intercept of the meta-analytic model, in other words, the estimated effect of typicality on the acoustic production of adjective-noun combinations).
<!-- TR: remove reference to meta-analytical estimate -->

@@

The nested model yields a posterior 95% CrI for between-team variability of `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of about `r pm(x = 0.1)` standard units and 95% probability.
The posterior 95% CrI for between-analysis variability (nested within teams) is `r round(meta_bm_nest_tidy$conf.low[["sd_animal:model_id__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal:model_id__Intercept"]], 2)` standard units ($\beta$ = 0.132, SD = 0.01).
Taken together, the models suggest that the variability of reported effects between any model (within team or across) is substantially larger than the variability across individual teams.
We return to this important observation later.

@@

<!-- TR: The meta analytical estimate is basically meaningless, given that the scale is not interpretable and artificial negative and positive estimates cancel each other out. I wonder whether we should take this out -->

Figure \@ref(fig:plot-meta1) illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
Given the nature and wide variety of acoustic operationalizations, there is no natural interpretation of the scale, so we cannot interpret the direction of estimates.
When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much estimates differed. 
Estimates ranged from `r round(min(msa_models$estimate),2)` to `r round(max(msa_models$estimate),2)` standard units. 
We will interpret these standard units relative to phonetic measures in the discussion section, but to provide an intuition about the absolute scale of variation, we can express them on a standardized scale that does not require domain expertise: The IQ scale [@kamphaus2019clinical] which is defined by a standard deviation of 15. 
The observed variability of estimates between teams corresponds to variability in IQ measures up to 14.9 IQ points.
While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e. are compatible with a point null hypothesis), there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (in blue, `r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).

@@

Different analysis paths led to different categorical conclusions with `r perc_atleast_1`% of teams reported to have found at least one statistically reliable effect.
To gain a better understanding of whether the observed quantitative variability can result in theoretically different claims, we will contextualize them in actual acoustic measures.
We calculated the standard deviation of a selection of acoustic measurements, as submitted by the analysis teams: duration, f0 and intensity, taken from different time windows. 
These standard deviations can be considered as a coarse indication of the variability in the obtained acoustic measures.
We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, f0 and intensity.^[Note that these categories necessarily refer to variegated sets of measures. E.g. the domain word includes words that differed along several dimensions, including their length and their metrical structure.]

>>>>

This section deals with the meta-analytic analysis of the results submitted by the teams.
<!-- TODO: repeat exclusion criteria -->
As discussed above, the analyses of only 30 teams out of all the submitted analysis were included in the meta-analytic model discussed here.
First, we report on the between-team variability estimate (i.e. the meta-analytic group-level standard deviation $\sigma_{\alpha_{\text{t}}}$), which is the focus of this study, followed by the meta-analytic estimate (i.e. the intercept of the meta-analytic model, in other words, the estimated effect of typicality on the acoustic production of adjective-noun combinations).
<!-- TR: remove reference to meta-analytical estimate -->

@@

The nested model yields a posterior 95% CrI for between-team variability of `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of about `r pm(x = 0.1)` standard units and 95% probability.
The posterior 95% CrI for between-analysis variability (nested within teams) is `r round(meta_bm_nest_tidy$conf.low[["sd_animal:model_id__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal:model_id__Intercept"]], 2)` standard units ($\beta$ = 0.132, SD = 0.01).
For the sake of illustration, these would correspond to an estimate of between-model variability in milliseconds (if looking for example at segment duration) that ranges between `r round(3.8*1.96, 1)` and `r round(7.7*1.96, 1)` ms at 95% credibility.
We discuss this in more details in the Discussion section.

Taken together, the models suggest that the variability of reported effects between any model (within team or across) is substantially larger than the variability across individual teams.
We return to this important observation later.

@@

<!-- TR: The meta analytical estimate is basically meaningless, given that the scale is not interpretable and artificial negative and positive estimates cancel each other out. I wonder whether we should take this out --> 
The meta-analytic intercept conflates estimates from a variety of responses taken from very different places in the utterance (nouns, adjectives, determiners, entire phrases or sentences, etc).
This means that some of the effects on a particular response as observed in a specific location within the utterance might naturally be positive, while other negative, resulting in a meta-analytic intercept of about zero.
We want to stress, however, that our focus is not on the meta-analytic intercept per se, but on the fact that a seemingly straightforward research question led to so many possible outcomes.
More on this in the Discussion section.

Figure \@ref(fig:plot-meta1) illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
Given the nature and wide variety of acoustic operationalizations, there is no natural interpretation of the scale, so we cannot interpret the direction of estimates.
When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much estimates differed. 
Estimates ranged from `r round(min(msa_models$estimate),2)` to `r round(max(msa_models$estimate),2)` standard units.

While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e. are compatible with a point null hypothesis), there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (in blue, `r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).

@@

Different analysis paths led to different categorical conclusions with `r perc_atleast_1`% of teams reported to have found at least one statistically reliable effect.
To gain a better understanding of whether the observed quantitative variability can result in theoretically different claims, we will contextualize them in actual acoustic measures.
We calculated the standard deviation of a selection of acoustic measurements, as submitted by the analysis teams: duration, f0 and intensity, taken from different time windows. 
These standard deviations can be considered as a coarse indication of the variability in the obtained acoustic measures.
We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, f0 and intensity.^[Note that these categories necessarily refer to a variegated set of measures, for example the domain "word" includes words that differed along several dimensions, including their length and their metrical structure.]
